Iterative Monomorphisation

### 2024-07-08 iterative_monomorphisation.tex
more

We see the following avenues for future work. First, iterative monomorphisation
blindly enumerates candidate instantiations, without exploiting any knowledge
about the logical structure of the formulas in which symbols occur. For
example, a lemma $\sym{p}\langle\alpha\rangle$ cannot be used to prove the
conjecture $\lnot \sym{p}\langle\ty{nat}\rangle$ because of the incompatible
polarities, but our procedure instantiates $\alpha$ with $\ty{nat}$ regardless.
Second, some automatic provers as well as tools like Sledgehammer include
a relevance filter that heuristically select a subset of the available axioms;
filters such as SInE \cite{xxx} and MePo \cite{xxx} are iterative and could be
interleaved with monomorphisation. Third, although one would expect native
implementations of polymorphism to outperform any preprocessor, our evaluation
clearly shows that this is not the case, therefore indicating that there is
considerable room for improvement on the native front.

>>>>

We see the following avenues for future work. First, iterative monomorphisation
blindly enumerates candidate instantiations, without exploiting any knowledge
about the logical structure of the formulas in which symbols occur. For
example, a lemma $\sym{p}\langle\alpha\rangle$ cannot be used to prove the
conjecture $\lnot \sym{p}\langle\ty{nat}\rangle$ because of the incompatible
polarities, but our procedure instantiates $\alpha$ with $\ty{nat}$ regardless.
Second, some automatic provers as well as tools like Sledgehammer include a
relevance filter that heuristically selects a subset of the available axioms;
filters such as MePo \cite{meng-paulson-2009} and SInE
\cite{hoder-voronkov-2011} are iterative and could be interleaved with
monomorphisation. Third, although one would expect native implementations of
polymorphism to outperform any preprocessor, our evaluation clearly shows that
this is not the case, therefore indicating that there is considerable room for
improvement on the native front.
